Matching bullets

### 2015-11-17 imaging-paper.Rnw
references to Thompson's work

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process. These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual.  }

3D topographical images were taken of these bullets using a NanoFocus lens at 20x magnification and made publicly available on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). 
x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. 
%The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. 
x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium\footnote{\url{http://www.openfmc.org/}}), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

Each fired bullet is provided as a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

>>>>

\hh{XXX here's a paragraph missing: rifling in the barrel is creating striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel - we need to find a citation for that from the SOP manual. Roger Thompson's writeup on firearm identification cites AFTE 1992 procedures.\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}} }

3D topographical images of each bullet were taken using a NanoFocus lens at 20x magnification and made publicly available on the NIST Ballistics Database Project\footnote{\url{http://www.nist.gov/forensics/ballisticsdb/hamby-consecutively-rifled-barrels.cfm}} in a format called x3p (XML 3-D Surface Profile). 
x3p is a container format conforming to the ISO5436-2 standard\footnote{\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}}, implemented to provide a simple and standard conforming way to exchange 2D and 3D profile data. 
%The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. 
x3p was adopted by the OpenFMC (Open Forensic Metrology Consortium\footnote{\url{http://www.openfmc.org/}}), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.
